Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-11 analysis/paper/paper.Rmd
Add figure as requested by @emdelponte of aggregated scores

>>>>

```{r article_scores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Aggregated article scores for each of the four categories. In subfigure `a`, `NA` indicates that no computational methods were used to generate the data, _e.g._ only PCR results were reported with no statistical analysis performed.', cache=FALSE, fig.env='figure'}
library("ggplot2")
library("patchwork")
rrpp <- import_notes()
theme_set(theme_classic())
a <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar() +
  ggtitle("Computational Methods Availability") +
  ylab("Score") +
  xlab(NULL)

b <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar() +
  ggtitle("Software Availability") +
  xlab(NULL) +
  ylab(NULL)

c <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar() +
  ggtitle("Software Cited") +
  ylab("Score")

d <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar() +
  ggtitle("Data Availability") +
  ylab(NULL)

# put them all together
p <- (a | b) / (c | d)
p + plot_annotation(tag_levels = "a")
```
